Textbook Knowledge on Hospital Information Management as Linked Data

### 2019-12-06 paper.tex
Add missing images and reference to FJ's medinfo paper.

In order to encourage and enable other researchers, students and health informatics professionals to use available knowledge of HIS management, we answer the following questions in this paper:
\todo{add questions}
We introduce different user interfaces to the SNIK ontology and discuss their suitability for different use cases of the target audiences.
%We discuss advantages and disadvantages of the interfaces and give recommendations on which ones present the best compromise for different use cases and target audiences.
We conclude with plans for future work on interlinking and visualization.

@@

\begin{figure}
\caption{SNIK Graph Overview}
\label{fig:snik-graph-overview}
\includegraphics[width=\columnwidth]{img/snik-graph.png}
\end{figure}

\begin{figure}
\caption{A teacher prepares a lecture on strategic HIS directing using the \enquote{Circle Star} function of SNIK Graph.}
\label{fig:snik-graph-circle-star}
\includegraphics[width=\columnwidth]{img/snik-graph-circle-star.png}
\end{figure}

@@

\section{Acknowledgments}
This work is supported by the DFG (German Research Foundation) under the Projects SNIK, grant no. 1605/7-1 and 1387/8-1, as well as HITO, grant no. WI 1605/11-1 and I3726-N31.
%We thank the publishers ... and ... for granting us permission to publish the subontologies based on the textbooks \citet{bb,ob,he} under an open license.
%\nocite{*} 
\todo{FJ: Hmmm, ziemlich selbstreferenziell. Brauchen wir da wirklich so viele Publikationen von uns? Welche anderen könnte man noch einbringen? Ich schaue auch mal, was mir so über den Weg läuft.}
\bibliographystyle{ios1}
\bibliography{paper,snik}
\section{Notes to Reviewers}
This paper includes and extends text and figures from:
- SNIK Graph: \todo{include medinfo poster reference}

>>>>

In order to encourage and enable other researchers, students and health informatics professionals to use available knowledge of HIS management, We introduce different user interfaces to the SNIK ontology and discuss their suitability for different use cases of the target audiences.
%We discuss advantages and disadvantages of the interfaces and give recommendations on which ones present the best compromise for different use cases and target audiences.
We conclude with plans for future work on interlinking and visualization.

@@

\begin{figure}
\caption{SNIK Graph Overview. Source: \protect\citet{snikgraph}.}
\label{fig:snik-graph-overview}
\includegraphics[width=\columnwidth]{img/snik-graph.png}
\end{figure}

\begin{figure}
\caption{A teacher prepares a lecture on strategic HIS directing using the \enquote{Circle Star} function of SNIK Graph. Source: \protect\citet{snikgraph}.}
\label{fig:snik-graph-circle-star}
\includegraphics[width=\columnwidth]{img/snik-graph-circle-star.png}
\end{figure}

@@

\section{Acknowledgments}
This work is supported by the DFG (German Research Foundation) under the Projects SNIK, grant no. 1605/7-1 and 1387/8-1, as well as HITO, grant no. WI 1605/11-1 and I3726-N31.
%We thank the publishers ... and ... for granting us permission to publish the subontologies based on the textbooks \citet{bb,ob,he} under an open license.
%\nocite{*} 
\todo{FJ: Hmmm, ziemlich selbstreferenziell. Brauchen wir da wirklich so viele Publikationen von uns? Welche anderen könnte man noch einbringen? Ich schaue auch mal, was mir so über den Weg läuft.}
\bibliographystyle{ios1}
\bibliography{paper,snik}
\section{Notes to Reviewers}
This paper includes and extends text and figures from:
\citet{snikgraph}
